Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2017-07-04 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add sentence describing drat from our paper

Some studies (e.g., @Zandbergen2009, @Czajkowski2011) assumed symmetrical activity of storm-related factors,which is not a realistic assumption for storm wind and rain patterns, particularly at and following landfall [@Kruk2010, @Halverson2015, @Rezapour2014].

@@

Currently, distance parameters involved with assessing risk of a particular storm have been rather arbitrary, contributing to the necessity in understanding how such parameters influence a county's exposure status. In assessing the risk of a given storm based on distance, recent studies have defined the distance from the storm track affected by a given storm differently. @Czajkowski2011 assessed county-level risk and exposure based on a three-tierd definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary coutnies, and tertiary counties adjacent to secondary counties. Such a definition resulted in an exposure defenition based on an average distance radius of 120 km [75 miles] on either side of the storm track [@Czajkowski2011]. Such a distance is slightly larger than that commonly used by public health departments (i.e., 100 km) [@Czajkowski2011].

@@

Distance-based measures that are based on a storm track passing through a county can also miss exposures from storms when they are offshore but near enough to the coast to cause important hazards to health and property (e.g., Agnes in 1972, FLoyd in 1999, Chantal in 1989) [@Czajkowski2011]. By basing the distance criteria on distance from the storm's track to county centers, more of these offshore storm exposures could be captured.

>>>>

Some studies (e.g., @Zandbergen2009, @Czajkowski2011) assumed symmetrical activity of storm-related factors, which is not a realistic assumption for storm wind and rain patterns, particularly at and following landfall [@Kruk2010, @Halverson2015, @Rezapour2014].

@@

To date, distance parameters involved with assessing risk of a particular storm have been rather arbitrary, contributing to the necessity in understanding how such parameters influence a county's exposure status. In assessing the risk of a given storm based on distance, recent studies have defined the distance from the storm track affected by a given storm differently. @Czajkowski2011 assessed county-level risk and exposure based on a three-tierd definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary coutnies, and tertiary counties adjacent to secondary counties. Such a definition resulted in an exposure defenition based on an average distance radius of 120 km [75 miles] on either side of the storm track [@Czajkowski2011]. Such a distance is slightly larger than that commonly used by public health departments (i.e., 100 km) [@Czajkowski2011].

@@

Distance-based measures that are based on a storm track passing through a county can also miss exposures from storms when they are offshore but near enough to the coast to cause important hazards to health and property (e.g., Agnes in 1972, Floyd in 1999, Chantal in 1989) [@Czajkowski2011]. By basing the distance criteria on distance from the storm's track to county centers, more of these offshore storm exposures could be captured.
